---
title: 'Project2: EDA on Retail'
author: "sourabh jain"
date: "08/11/2020"
output: html_document
---


### Loading and exploring the data 
```{r}
# Reading the data
superstore<-read.csv("SampleSuperstore.csv")
#names of column

names(superstore)

#structure of the data
str(superstore)

# checking if there is any missing value which is represented by NA
colSums(is.na(superstore))
## There are no missing values

#Summary: to find statistical values for each variable
summary(superstore)

#total quantity
sum(superstore$Quantity)

#total Sale
sum(superstore$Sales)

#total Profit
sum(superstore$Profit)
```
### Exploratory Data Analysis
#### Understanding the data with tables and graphs

```{r}
#studying Ship mode
library(ggplot2)
table(superstore$Ship.Mode)
ggplot(data=superstore,aes(x=Ship.Mode,fill=Ship.Mode))+geom_bar(width=0.5)
```

#### Observation 1: Maximum customer prefer Standard Class as the ship mode. 

```{r}
#Studying Segment
table(superstore$Segment)
ggplot(data=superstore,aes(x=Segment,fill=Segment))+geom_bar(width = 0.5)

#Studying Region
table(superstore$Region)
ggplot(data=superstore,aes(x=Region,fill=Region))+geom_bar(width = 0.5)
```

#### Observation 2: Maximum customers are from West region and minimum are from South



```{r}
#studying category
table(superstore$Category)
ggplot(data=superstore,aes(x=Category,fill=Category))+geom_bar(width = 0.5)

#studying categories ans sub
table(superstore$Sub.Category,superstore$Category)
ggplot(data=superstore,aes(x=Sub.Category,fill=Sub.Category))+geom_bar()+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))

```


#### Observation 3: The maximum sub categories are from Binders, paper, Furnishings and minimum are from Supplies, MAchines and Copiers

```{r}
ggplot(data=superstore,aes(x=State))+geom_bar()+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
```

#### Observation 4: Highest number of buyers are from California and New YOrk.

```{r}
ggplot(data=superstore,aes(x=Quantity))+geom_bar()
```

#### Observation 5. Most people tends to buy Quantity of 2-3

```{r}
ggplot(data=superstore,aes(x=Segment,y=Sales,fill=Segment))+geom_bar(stat="identity",width = 0.5)
```

#### Observation 6. The maximum sales is in the consumer segment and minimum sales is in Home Office segment

```{r}
# profit evaluation 
superstore1<-superstore[superstore$Profit>0,]
ggplot(data=superstore1,aes(x=Segment,y=Profit,fill=Segment))+geom_bar(stat="identity",width=0.5)
```

#### Observation 7. The maximum profit is from Consumer Segment

```{r}
# Sales and Profit Evaluation Regionwise
ggplot(data=superstore,aes(x=Region,y=Sales,fill=Region))+geom_bar(stat="identity",width=0.5)
ggplot(data=superstore1,aes(x=Region,y=Profit,fill=Region))+geom_bar(stat="identity",width = 0.5)
```

#### Observation 8. The maximum sales is in West region but the maximum profit is in East region


```{r}
# Sales Evvaluation of Categories and Sub categories
ggplot(data=superstore,aes(x=Category,y=Sales,fill=Category))+geom_bar(stat="identity",width=0.5)
ggplot(data=superstore,aes(x=Sub.Category,y=Sales,fill= Sub.Category))+geom_bar(stat="identity")+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
```

#### Observation 9. There has been maximum sales in Technology Category than Office Supplies and Furniture Category.

#### Observation 10. There has been Maximum sale of Phones and chairs while Fasteners and Labels has the minimum sales. '

```{r}
ggplot(data=superstore1,aes(x=Category,y=Profit, fill=Category)) + geom_bar(stat="identity",width=0.5)
ggplot(data=superstore1,aes(x=Sub.Category,y=Profit,fill= Sub.Category))+geom_bar(stat="identity")+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
```

#### Observation 11. Technology and Office Supplies Category gave the maximum profit

#### Observation 12. Max profit are from Blinders, Phones and Copiers while minimum profit is from fasteners and Suppliers category

```{r}
# Discount Analysis
ggplot(data=superstore,aes(x=Category,y=Discount,fill=Category))+geom_bar(stat="identity",width=0.5)
ggplot(data=superstore,aes(x=Sub.Category,y=Discount ,fill= Sub.Category))+geom_bar(stat="identity")+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
```

#### Observation 13. Office Suplies Category was given maximum discount
#### Observation 14. In sub Category BLinders were sold with maximum discount. 

```{r}
ggplot(data=superstore,aes(x=State,y=Sales))+geom_bar(stat="identity",width=0.5)+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
ggplot(data=superstore1,aes(x=State,y=Profit))+geom_bar(stat="identity",width=0.5)+theme(axis.text.x = element_text(angle=90,hjust = 1,vjust = 1))
```

#### Observation 15. Sales and Profit are maximum in California and New York city. 


